Fig2

### 2020-03-26 analysis/figure-2.Rmd
one less candidate gene

candidategenes <- c("OXT", "AVP", "GNRH1", "GNRHR", "CGNRH-R",
                    "AR",  "CYP19A1", 
                     "AVPR1A", "AVPR1B", "AVPR2","VIP",
                  "DRD1", "DRD2", 
                  "PRL", "PRLR",  
                    "ESR1","ESR2", "LBH",

>>>>

candidategenesslim <- c("OXT", "AVP", "GNRH1", "GNRHR", 
                    "AR",  "CYP19A1", 
                     "AVPR1A", "AVPR1B", "AVPR2","VIP",
                  "DRD1", "DRD2", 
                  "PRL", "PRLR",  
                    "ESR1","ESR2", "LBH",
